DeepSphere: a graph-based spherical CNN

### 2019-09-24 main.tex
unify notation: n for number of pixels

\todo{
\begin{itemize}
	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN.
	\item adjacency matrix: $A$ instead of $W$?
	\item anonymize DeepSphere citation
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot
	\item result tables: only what supports the main message in the text, everything we have in the appendix
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions.
\end{itemize}
}
\newpage

@@

% 3.0) explain how we obtained the figures
We calculated numerically the equivariance error (\ref{eq:mean equivariance error}) by generating $N$ monochromatic signals and $M$ random rotations for each signal. The colors that were used were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the rotated signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_V$ (\cite{healpix_primer})

@@

The SHREC'17 shape retrieval contest \citep{shrec17} contains 51,300 randomly oriented 3D models from ShapeNet \citep{shapenet}, to be classified in 55 categories (tables, lamps, airplanes, etc.).
As in \citet{cohen2018sphericalcnn}, objects are represented by 6 spherical maps.
At each pixel, a ray is traced towards the center of the sphere.
The distance from the sphere to the object forms a depth map.
The $\cos$ and $\sin$ of the surface angle forms two normal maps.
The same is done for the object's convex hull.\footnote{Albeit we didn't observe much improvement by using the convex hull.}
The maps are discretized using either an equiangular grid \citep{driscoll1994Fouriersphere} with bandwidth $b = 64$ ($N_{pix} = 4 b^2 = 16,384$), or an HEALPix \citep{healpix} grid with $N_{side} = 32$ ($N_{pix} = 12 N_{side}^2 = 12,288$).

@@

Given observations, cosmologists estimate the posterior probability of cosmological parameters, such as the matter density $\Omega_m$ and the normalization of the matter power spectrum $\sigma_8$.
Those parameters are typically estimated by likelihood-free inference, which requires a function to predict the parameters from simulations.
% such as Approximate Bayesian computation (ABC)
As that is complicated to setup, prediction methods are typically benchmarked on the classification of spherical maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}.
We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps ($1/12 \approx 8\%$ of the sphere) made of $10^6$ pixels from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $4$.
% 60 maps * 12 parts = 720 parts
Convergence maps represent the distribution of over- and under-densities of mass in the universe \citep[see][for a review of gravitational lensing]{bartelman2010gravitationallensing}.

@@

We evaluate our method on a task proposed by \citep{mudigonda2017climateevents}: the segmentation of extreme climate events, Tropical Cyclones (TC) and Atmospheric Rivers (AR), in global climate simulations (\figref{examples:climate}).
The data was produced by a 20-year run of the Community Atmospheric Model v5 (CAM5) and consists of 16 channels such as temperature, wind, humidity, and pressure at multiple altitudes.
We used the pre-processed dataset from \citep{jiang2019sphericalcnn}.\footnote{Available at \url{http://island.me.berkeley.edu/ugscnn/data}.}
%\url{https://github.com/maxjiang93/ugscnn}
%\url{https://github.com/maxjiang93/ugscnn/blob/master/experiments/exp4_sphere_climate/run.sh}
%\url{http://island.me.berkeley.edu/ugscnn/data/climate_sphere_l5.zip}
There is 1,072,805 spherical maps, down-sampled to a level-5 icosahedral grid ($N_{pix} = 10 \cdot 4^l + 2 = 10,242$).
The labels are heavily unbalanced with 0.1\% TC, 2.2\% AR, and 97.7\% background (BG) pixels.

@@

To demonstrate the flexibility of modeling the discretized sphere by a graph, we collected historical measurements from about 10,000 weather stations scattered across the Earth.\footnote{\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
The spherical data is heavily non-uniformly sampled, with a much higher density of weather stations over North America than the Pacific (\figref{examples:ghcn:tmax}).
For illustration, we devised two artificial tasks.
A dense regression that consists of predicting the temperature on a given day knowing the temperature on the 5 previous days.
A global regression that consists of predicting the day (represented as one period of a sine over the year) from temperature or precipitations.

>>>>

\todo{
\begin{itemize}
	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN.
	\item adjacency matrix: $A$ instead of $W$?
	\item anonymize DeepSphere citation
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method.
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot
	\item result tables: only what supports the main message in the text, everything we have in the appendix
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions.
	\item unify enumerations. I like (i), (ii), etc.
\end{itemize}
}
\newpage

@@

% 3.0) explain how we obtained the figures
We calculated numerically the equivariance error (\ref{eq:mean equivariance error}) by generating $N$ monochromatic signals and $M$ random rotations for each signal. The colors that were used were chosen in the range $(0,\  3N_{side}-1)$ to allow for an almost perfect synthesis of the rotated signals, and thus an almost perfect implementation (up to numerical errors) of the operator $\b{R}_V$ \citep{healpix_primer}.

@@

The SHREC'17 shape retrieval contest \citep{shrec17} contains 51,300 randomly oriented 3D models from ShapeNet \citep{shapenet}, to be classified in 55 categories (tables, lamps, airplanes, etc.).
As in \citet{cohen2018sphericalcnn}, objects are represented by 6 spherical maps.
At each pixel, a ray is traced towards the center of the sphere.
The distance from the sphere to the object forms a depth map.
The $\cos$ and $\sin$ of the surface angle forms two normal maps.
The same is done for the object's convex hull.\footnote{Albeit we didn't observe much improvement by using the convex hull.}
The maps are discretized using either an equiangular grid \citep{driscoll1994Fouriersphere} with bandwidth $b = 64$ ($n = 4 b^2 = 16,384$ pixels), or an HEALPix \citep{healpix} grid with $N_{side} = 32$ ($n = 12 N_{side}^2 = 12,288$ pixels).

@@

Given observations, cosmologists estimate the posterior probability of cosmological parameters, such as the matter density $\Omega_m$ and the normalization of the matter power spectrum $\sigma_8$.
Those parameters are typically estimated by likelihood-free inference, which requires a function to predict the parameters from simulations.
% such as Approximate Bayesian computation (ABC)
As that is complicated to setup, prediction methods are typically benchmarked on the classification of spherical maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}.
We used the same task, data, and setup as \citet{perraudin2019deepspherecosmo}: the classification of $720$ partial convergence maps ($1/12 \approx 8\%$ of the sphere) made of $n \approx 10^6$ pixels from two $\Lambda$CDM cosmological models, ($\Omega_m = 0.31$, $\sigma_8 = 0.82)$ and ($\Omega_m = 0.26$, $\sigma_8 = 0.91)$, at a relative noise level of $4$.
% 60 maps * 12 parts = 720 parts
Convergence maps represent the distribution of over- and under-densities of mass in the universe \citep[see][for a review of gravitational lensing]{bartelman2010gravitationallensing}.

@@

We evaluate our method on a task proposed by \citep{mudigonda2017climateevents}: the segmentation of extreme climate events, Tropical Cyclones (TC) and Atmospheric Rivers (AR), in global climate simulations (\figref{examples:climate}).
The data was produced by a 20-year run of the Community Atmospheric Model v5 (CAM5) and consists of 16 channels such as temperature, wind, humidity, and pressure at multiple altitudes.
We used the pre-processed dataset from \citep{jiang2019sphericalcnn}.\footnote{Available at \url{http://island.me.berkeley.edu/ugscnn/data}.}
%\url{https://github.com/maxjiang93/ugscnn}
%\url{https://github.com/maxjiang93/ugscnn/blob/master/experiments/exp4_sphere_climate/run.sh}
%\url{http://island.me.berkeley.edu/ugscnn/data/climate_sphere_l5.zip}
There is 1,072,805 spherical maps, down-sampled to a level-5 icosahedral grid ($n = 10 \cdot 4^l + 2 = 10,242$ pixels).
The labels are heavily unbalanced with 0.1\% TC, 2.2\% AR, and 97.7\% background (BG) pixels.

@@

To demonstrate the flexibility of modeling the discretized sphere by a graph, we collected historical measurements from about $n = 10,000$ weather stations scattered across the Earth.\footnote{\url{https://www.ncdc.noaa.gov/ghcn-daily-description}}
The spherical data is heavily non-uniformly sampled, with a much higher density of weather stations over North America than the Pacific (\figref{examples:ghcn:tmax}).
For illustration, we devised two artificial tasks.
A dense regression that consists of predicting the temperature on a given day knowing the temperature on the 5 previous days.
A global regression that consists of predicting the day (represented as one period of a sine over the year) from temperature or precipitations.
